Abstractions for Multi-Sorted Substitutions

### 2023-09-19 paper/paper.tex
Update.

@@

  \subsection{WkKits}
  \label{sec:composition:wkkit}

  Before we define \ACode{\ACon{ComposeKit}} and
  \ACode{\ACon{ComposeTraversal}}, we need one more ingredient.

  In the definition of \ACode{\ACon{Kit}} we required the axiom
  \ACode{\AField{wk-id/`}}, which captured the interaction between
  \ACode{\AField{wk}} and \ACode{\AField{id/`}}:
  \ExampleCode{\KWkId}
  Injecting a variable with \ACode{\AField{id/`}} and then shifting it,
  is the same as injecting a shifted variable.

  Now that we have defined the \ACode{\ACon{Traversal}} structure, we
  can formulate a similar interaction between
  \ACode{\AField{wk}} and \ACode{\AField{`/id}}:
  \ExampleCode{\KIdWk}
  Shifting a variable/term \ACode{x/t} with \ACode{\AField{wk}} and then injecting
  it to a term, is the same as injecting \ACode{x/t} to a term and then applying
  a shifting renaming.
  Instead of explaining \ACode{\AField{wk}} through its action on variables,
  this lemma explains \ACode{\AField{wk}} through its action on terms.

  As this lemma depends on map application \ACode{\ADef{\_⋯\_}} being
  already defined, we cannot add it to the original \ACode{\ACon{Kit}}
  structure, but need to define a new structure for it, which we call
  a \ACode{\ACon{WkKit}}:
  \LibCode\KWkKit

  We then create exactly two instances of the \ACode{\ACon{WkKit}} for
  the variable and term kit, respectively. 
  \LibCode\KWkKitInstances

  Both the structure and the instances are part of the library and do
  not require application code.

  \subsection{Composition}
  \label{sec:composition:ckit}

>>>>

  \subsection{Extension Kits}
  \label{sec:maps:wkkit}

  % Before we define \ACode{\ACon{ComposeKit}} and
  % \ACode{\ACon{ComposeTraversal}}, we need one more ingredient.

  As we defined the \ACode{\ACon{Kit}} structure before the
  \ACode{\ACon{Traversal}} structure, the fields of
  \ACode{\ACon{Kit}} could not use the \ACode{\ACon{\_⋯\_}} function in
  their types.

  This prevented us to define a useful lemma, which also needs to
  be instanciated separately for variables and terms: the counterpiece
  to \ACode{\AField{wk-id/`}}, which we call \ACode{\AField{wk-`/id}}.

  Recall that \ACode{\AField{wk-id/`}} explains the
  \ACode{\AField{wk}} function of an arbitrary \ACode{\ACon{Kit}} by how it acts on
  \emph{variables}:
  \ExampleCode{\KWkId}

  Similarly, the \ACode{\AField{wk-`/id}} lemma
  explains the \ACode{\AField{wk}} function of an
  arbitrary \ACode{\ACon{Kit}} by how it acts on \emph{terms}:
  \ExampleCode{\KIdWk}

  This lemma is useful for proving extensional equalities between maps
  involving weakening, where \ACode{\AField{`/id-injective}} allows to
  add \ACode{\AField{`/id}} on both sides of the equation, such that
  \AField{wk-`/id} can be used to make further progress.

  To prove \AField{wk-`/id}, we define a structure
  \ACode{\ACon{WkKit}}, which extends a regular \ACode{\ACon{Kit}} with
  the \AField{wk-`/id} lemma:
  \LibCode\KWkKit

  We then create exactly two instances of the \ACode{\ACon{WkKit}} for
  the variable and term \ACode{\ACon{Kit}}, respectively. 
  \LibCode\KWkKitInstances

  As the variable and term \ACode{\ACon{Kit}}s are the only two \ACode{\ACon{Kit}}s,
  and both have \ACode{\ACon{WkKit}} instances, it is always safe to assume that
  a \ACode{\ACon{Kit}} also supports the \ACode{\ACon{WkKit}} extension.

  % Both the structure and the instances are part of the library and do
  % not require application code.

@@

  \subsection{An Abstraction for Composition}
  \label{sec:composition:ckit}
